

####Read in data

```{r}
library(ggplot2)
library(caret)
library(randomForest)
setwd("C:/Users/Lily/course8/project")
trainingdata <- read.csv("./pml-training.csv")
testdata <- read.csv("./pml-testing.csv")
```
#### Remove near zero covariates

```{r}
nearzero <- nearZeroVar(trainingdata, saveMetrics = T)
trainingdata <- trainingdata[, !nearzero$nzv]
```

#####Remove variables with more than 80% missing 

```{r}
egvar <- sapply(colnames(trainingdata), function(x) if(sum(is.na(trainingdata[, x])) > 0.8*nrow(trainingdata)){return(T)}else{return(F)})

trainingdata <- trainingdata[, !egvar]
```

####Remove variables with more than 80% missing and subset

```{r}
egvar <- sapply(colnames(trainingdata), function(x) if(sum(is.na(trainingdata[, x])) > 0.8*nrow(trainingdata)){return(T)}else{return(F)})
trainingdata <- trainingdata[, !egvar]
trainingdata <- trainingdata[8:length(trainingdata)]
```

##### Split the cleaned testing data into training and cross validation

```{r}
inTrain <- createDataPartition(y = trainingdata$classe, p = 0.7, list = FALSE)
training <- trainingdata[inTrain, ]
crossval <- trainingdata[-inTrain, ]
```
#### Plot a correlation matrix

```{r, echo=FALSE}
correlMatrix <- cor(training[, -length(training)])
library(corrplot)
corrplot(correlMatrix, order = "FPC", method = "circle", type = "lower", tl.cex = 0.8,tl.col = rgb(0, 0, 0))

```

```{r}
model <- randomForest(classe ~ ., data = training)

```

#### Cossvalidate the model using the remaining 30% of data
Crossvalidate the model by using the 30% of the training data. 
From the output we can see this model generates a 99.3% prediction accuracy. 
So this model proved very robust and adequete to predict new data.
```{r}
predictCrossVal <- predict(model, crossval)
library(e1071)
confusionMatrix(crossval$classe, predictCrossVal)

```
#### Apply the same treatment to the final testing data
```{r}
data_test_NAs <- apply(testdata, 2, function(x) {sum(is.na(x))})
data_test_clean <- testdata[,which(data_test_NAs == 0)]
data_test_clean <- data_test_clean[8:length(data_test_clean)]

```
#### Predict the classes of the test set

```{r}
predictTest <- predict(model, data_test_clean)

pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}

pml_write_files(predictTest)

```

